\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2\baselineskip}

### 2016-09-29 document/ms.tex
finishing response to referee

We measure the empirical detection efficiency function of our search procedure
by injecting simulated transit signals into the target light curves and
measuring the recovery rate.
By combining the measured detection efficiency and the catalog of exoplanet
candidates, we estimate the integrated occurrence rate of exoplanets with
orbital periods in the range $2-25\unit{years}$ and radii in the range
$0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K dwarf.
\response{%
This result is qualitatively consistent with estimates of the occurrence rate
of long-period giant planets based on data from radial velocity and direct
imaging surveys.
The occurrence rate measured here~--~for Sun-like hosts~--~is higher than
microlensing results for lower mass stars \citep{Clanton:2014, Clanton:2016}
but this discrepancy is consistent with predictions from the core-accretion
model \citep{Laughlin:2004}.
}

@@

% \acknowledgments
\vspace{1.5em}
It is a pleasure to thank
Jeff Coughlin,
So Hattori,
Heather Knutson,
Phil Muirhead,
Darin Ragozzine,
Hans-Walter Rix,
Dun Wang,
and
Angie Wolfgang
for helpful discussions and contributions.

>>>>

We measure the empirical detection efficiency function of our search procedure
by injecting simulated transit signals into the target light curves and
measuring the recovery rate.
By combining the measured detection efficiency and the catalog of exoplanet
candidates, we estimate the integrated occurrence rate of exoplanets with
orbital periods in the range $2-25\unit{years}$ and radii in the range
$0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K dwarf.
\response{%
This result is qualitatively consistent with estimates of the occurrence rate
of long-period giant planets based on data from radial velocity and direct
imaging surveys.
The occurrence rate measured here~--~for Sun-like hosts~--~is higher than
microlensing results for generally lower mass stars \citep{Gaudi:2012,
Clanton:2014, Clanton:2016} but this discrepancy is consistent with
predictions from the core-accretion model \citep{Laughlin:2004}.
}

@@

% \acknowledgments
\vspace{1.5em}
It is a pleasure to thank
Jeff Coughlin,
So Hattori,
Heather Knutson,
Phil Muirhead,
Darin Ragozzine,
Hans-Walter Rix,
Dun Wang,
and
Angie Wolfgang
for helpful discussions and contributions.
We thank the anonymous referee for comments that improved the presentation and
clarity of this manuscript.
